\Title

### 2023-02-20 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

    	Representation of the weights for $3$ of the $32$ different learned kernels of the model as learned on natural scenes. Each pair of line correspond to the OFF and ON polarities respectively, with excitatory weights in warm colors. Delays are represented in the horizontal axis from right (zero delay) to the left (delay of $11$ steps). Because of the symmetry observed between the ON and OFF event streams, we observed that kernels are very similar for the ON polarities. These weights are associated to a specific delay on the \textit{delays} axis and to a presynaptic address defined on the two other axes. %	For the sake of clarity, the values in range $[-0.05, 0.05]$ are not shown. 
	Different kernels are selective to the different motion directions and we observe some level of orientation selectivity, where ON and OFF subfields organized in a push-pull organization. 
%        One sees positive (excitatory) coefficients for the specific direction of motion but also negative (inhibitory) coefficients for other directions.

>>>>

    	Representation of the weights for $8$ directions for one speed (among the $8 \times 3$ different kernels of the model) as learned on the dataset of naturalistic scenes. Directions are shown as red arrows on the left. The spatio-temporal kernels are represented as a sequence of images at different delays along the horizontal axis from the far right (delay of one step) to the left (delay of $12$ steps). Each image corresponds to the weights at a given delay, with excitatory and inhibitory weights in warm and cold colors, respectively. Due to the observed symmetry between the ON and OFF event streams, we observed that the kernels for the OFF polarities are very similar and are not shown here.	Different kernels are selective to the different motion directions and we observe a slight level of orientation selectivity perpendicular to the orientation. 
%      % These weights are associated to a specific delay on the \textit{delays} axis and to a presynaptic address defined on the two other axes. %	For the sake of clarity, the values in range $[-0.05, 0.05]$ are not shown.    One sees positive (excitatory) coefficients for the specific direction of motion but also negative (inhibitory) coefficients for other directions.
